Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
minor fix

For every imputation inserted into the query plan, a new statistical model is instantiated and trained before being used for imputation.
Although it is tempting to further optimize query execution in \ProjectName{} by pre-training imputation models while the analyst begins to make queries,
this is not desirable because the specific rows of data, set of complete attributes, and set of attributes to impute are not known until runtime.

>>>>

For every imputation inserted into the query plan, a new statistical model is instantiated and trained before being used for imputation.
Although it is tempting to further optimize query execution in \ProjectName{} by pre-training imputation models while the analyst begins to make queries,
this is not desirable because the specific rows of data, set of complete attributes, and set of attributes to impute are unknown until runtime.
